---
title: "A UN Report on the Relationship between GDP and Life Expectancy"
author: "Sharon"
date: "2023-05-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse)
```

This report was prepared to the attention of the UN. It analyzes the relationships between a country's GFP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country's economic strength or weakness may be related to its public...

```{r load data, include=FALSE}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```

```{r gdp_lifeexp_1997, echo=FALSE}
ggplot(data = gapminder_1997) + 
  aes(x= gdpPercap, y = lifeExp, color = continent, size=pop/1000000) +
  geom_point() +
  labs(x= "GDP Per Capita", y="Life Expectancy", 
       title = "DO people in wealth countries life longer",
       size= "Population (in millions)")
```
```{r, include=FALSE}
# this piece of code count the number of countries
nCountries <- gapminder_1997 %>% select(country) %>% n_distinct()
minGDP <- gapminder_1997 %>% summarise(min(gdpPercap)) %>% 
   pull()
maxGDP <-gapminder_1997 %>% summarise(max(gdpPercap)) %>% 
   pull()
```

The above plot shows the relationship betwen GDP and life expectancy for a total of `r nCountries` countries. 
For this set of countriess, economic wealth ranged from a min of USD
`r minGDP` to `r maxGDP`

| HEADER 1 | HEADER 2 |
| -------- | -------- |
| row 1, column 1 | row 1, column 2 |
| row 2, column 1 | row 2, column 2 |

```{r kable_table}
library(knitr)
gapminder_1997 %>% 
  filter(continent == "Oceania") %>% 
  kable() #function for making a table
```



